% =============================================================
%   PROJECT DIARY REPORT — END SEMESTER EVALUATION
%   Minor Project (Phase-II), B.Tech 6th Semester
%   Dr. B. R. Ambedkar National Institute of Technology Jalandhar
%   Department of Instrumentation and Control Engineering
% =============================================================
\documentclass[12pt,a4paper,oneside]{report}

% ─── Packages ────────────────────────────────────────────────
\usepackage[margin=1in,top=1.2in,bottom=1.2in]{geometry}
\usepackage{times}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{parskip}
\usepackage{microtype}

% ─── Line Spacing ────────────────────────────────────────────
\onehalfspacing

% ─── Header / Footer ─────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\rhead{\small Intelligent Pesticide Sprinkling System}
\lhead{\small Project Diary Report}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

% ─── Custom Commands ─────────────────────────────────────────
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}

% A reusable weekly diary block: one row per heading, one line each.
\newcommand{\diaryblock}[5]{%
\renewcommand{\arraystretch}{1.5}%
\noindent\begin{tabularx}{\textwidth}{|p{4.6cm}|X|}
\hline
\textbf{Objectives Planned} & #1 \\
\hline
\textbf{Work Executed During the Week} & #2 \\
\hline
\textbf{Discussion and Feedback from Supervisor} & #3 \\
\hline
\textbf{Issues and Challenges Identified} & #4 \\
\hline
\textbf{Action Plan for Next Week} & #5 \\
\hline
\end{tabularx}%
}

% =============================================================
\begin{document}
\pagestyle{empty}

% ─── Title Block ─────────────────────────────────────────────
\begin{center}
\vspace*{0.4cm}
{\large \textbf{PROJECT DIARY REPORT}}\\[0.2cm]
{\normalsize END SEMESTER EVALUATION (PHASE -- II)}\\[0.5cm]
\HRule\\[0.25cm]
{\large \textbf{Intelligent Pesticide Sprinkling System\\
Determined by the Infection Level of Plants}}\\[0.25cm]
\HRule\\[0.6cm]
\end{center}

\renewcommand{\arraystretch}{1.3}
\noindent\begin{tabularx}{\textwidth}{p{4.2cm}X}
\textbf{Submitted by} & Bhavesh Singh (23106030), Chahat Kesharwani (23106032), \\
 & Sadgi Saraswat (23106078), Vanshika Soni (23106099) \\[0.2cm]
\textbf{Supervisor} & Dr. Karan Veer, Assistant Professor, Dept. of ICE \\[0.2cm]
\textbf{Total Duration} & 9 Weeks (Weeks 1--4 evaluated at Mid-Semester) \\[0.2cm]
\textbf{Coverage of this Report} & Weeks 5--9 (Final 60\% of project work) \\
\end{tabularx}

\vspace{0.4cm}
\noindent\textit{The first four weeks, presented during the mid-semester evaluation, covered the
initial 40\% of the project, comprising literature study, dataset preparation, model
finalisation, base circuit design, and preliminary subsystem testing. The remaining 60\% of the
work, reported below, focuses on hardware enclosure assembly, integration of the pump/sprayer
mechanism, completion of the web dashboard, end-to-end workflow testing, and final prototype
readiness for demonstration.}

\vspace{0.6cm}

% =============================================================
%  WEEK 5 & 6
% =============================================================
\noindent\textbf{\large Week 5 \& Week 6 (Combined)}
\vspace{0.2cm}

\diaryblock
{To assemble all hardware components inside a compact enclosure and integrate the sprayer mechanism with the control system.}
{Mounted and wired the components within the enclosure and integrated the sprayer mechanism, verifying spraying response against infection severity.}
{The supervisor appreciated the neat enclosure layout and advised proper wire management and severity-based calibration.}
{Loose connections caused intermittent operation and the nozzle initially produced an uneven spray pattern.}
{To complete the web dashboard and begin integrated testing of the full image-capture-to-spraying workflow.}

\vspace{0.8cm}

% =============================================================
%  WEEK 7, 8 & 9
% =============================================================
\noindent\textbf{\large Week 7, Week 8 \& Week 9 (Combined)}
\vspace{0.2cm}

\diaryblock
{To complete the web dashboard and prepare a tested final prototype for demonstration and evaluation.}
{Completed the web dashboard and integrated the full image-capture-to-severity-based-spraying workflow, tested on healthy and infected leaf samples.}
{The supervisor confirmed the workflow met the objectives and recommended minor UI refinements and additional test runs.}
{Varying lighting affected severity consistency and dashboard readings needed synchronisation with the spraying action.}
{To carry out final calibration, documentation, and demonstration of the completed prototype for the end-semester evaluation.}

\vspace{0.8cm}

\noindent\textbf{Summary:} By the end of Week 9, the prototype was fully assembled within a compact
hardware enclosure, the sprayer mechanism was integrated with the control system, the web dashboard
was operational, and the complete image-capture-to-spraying workflow was tested and ready for
demonstration --- completing the remaining 60\% of the project beyond the 40\% achieved at the
mid-semester stage.

\vspace{1.2cm}
\renewcommand{\arraystretch}{1.3}
\noindent\begin{tabularx}{\textwidth}{p{0.45\textwidth}X}
\rule{5cm}{0.4pt} & \hfill\rule{5cm}{0.4pt} \\
Signature of Students & \hfill Signature of Supervisor \\
 & \hfill Dr. Karan Veer \\
\end{tabularx}

\end{document}
